Evaluation of classical correlation functions from 2/3D images on CPU and GPU architectures: introducing CorrelationFunctions.jl

### 2023-05-16 paper-correlations.tex
Redraw plots for real XCT samples

\section{Examples and applications}
\label{sec:examples}
After the verification of our computational approach based on analytical
solution we can apply our algorithms to evaluate correlation functions for
different porous media images, including real XCT and SEM images. A summary
which contains information about type of the images, dimensions and resolution
can be found in \cref{tab:samples}. XCT images of sandstones are provided by
Digital Rocks Portal\cite{DigitalRocks}. Correlation functions of these samples
can be seen on \cref{fig:real-data}.

\begin{table*}[!pt]
  \centering
  \begin{ruledtabular}
    \begin{tabular}{|c|c|c|c|}
      Sample name & Image type & Dimensions (pixels) & Image resolution ($\mu m$) \\
      \hline
      Bandera Brown sandstone & XCT & $1000 \times 1000 \times 1000$ & 2.25 \\
      Bentheimer sandstone    & XCT & $1000 \times 1000 \times 1000$ & 2.25 \\
      Kirby sandstone         & XCT & $1000 \times 1000 \times 1000$ & 2.25 \\
      Sandstone 1 & SEM &  $1280 \times 869$ & 0.10 \\
      Sandstone 2 & SEM &  $1280 \times 869$ & 0.05 \\
      Carbonate 1 & SEM &  $1024 \times 691$ & 0.06
    \end{tabular}
  \end{ruledtabular}
  \caption{Summary of samples used for calculation of correlation functions.}
  \label{tab:samples}
\end{table*}

\begin{figure*}[pt]
  \centering
  \subfigure[Bandera Brown sandstone]{
    \includegraphics[width=0.3\linewidth]{real-data/BanderaBrown_2d25um_binary.png}
    \label{fig:bandera}}
  \hfill
  \subfigure[Bentheimer sandstone]{
    \includegraphics[width=0.3\linewidth]{real-data/Bentheimer_2d25um_binary.png}
    \label{fig:bentheimer}}
  \hfill
  \subfigure[Kirby sandstone]{
    \includegraphics[width=0.3\linewidth]{real-data/Kirby_2d25um_binary.png}
    \label{fig:kirby}}
  \vskip\baselineskip
  \subfigure[Bandera Brown sandstone (correlation functions)]{
    \includegraphics[width=0.3\linewidth]{real-data/BanderaBrown_2d25um_binary-plot.png}
    \label{fig:bandera-plt}}
  \hfill
  \subfigure[Bentheimer sandstone (correlation functions)]{
    \includegraphics[width=0.3\linewidth]{real-data/Bentheimer_2d25um_binary-plot.png}
    \label{fig:bentheimer-plt}}
  \hfill
  \subfigure[Kirby sandstone (correlation functions)]{
    \includegraphics[width=0.3\linewidth]{real-data/Kirby_2d25um_binary-plot.png}
    \label{fig:kirby-plt}}
  \vskip\baselineskip
  \subfigure[Sandstone 1]{
    \includegraphics[width=0.3\linewidth]{real-data/sandstone1.png}
    \label{fig:real-sandstone-1}}
  \hfill
  \subfigure[Sandstone 2]{
    \includegraphics[width=0.3\linewidth]{real-data/sandstone2.png}
    \label{fig:real-sandstone-2}}
  \hfill
  \subfigure[Carbonate 1]{
    \includegraphics[width=0.3\linewidth]{real-data/carbonate1.png}
    \label{fig:real-carbonate-1-plt}}
  \vskip\baselineskip
  \subfigure[Sandstone 1 (correlation functions)]{
    \includegraphics[width=0.3\linewidth]{real-data/sandstone1-plot.png}
    \label{fig:real-sandstone-1-plt}}
  \hfill
  \subfigure[Sandstone 2 (correlation functions)]{
    \includegraphics[width=0.3\linewidth]{real-data/sandstone2-plot.png}
    \label{fig:real-sandstone-2-plt}}
  \hfill
  \subfigure[Carbonate 1 (correlation functions)]{
    \includegraphics[width=0.3\linewidth]{real-data/carbonate1-plot.png}
    \label{fig:real-carbonate-1}}
  \caption[]{Plots of correlation functions for real samples.}
  \label{fig:real-data}
\end{figure*}

>>>>

\section{Examples and applications}
\label{sec:examples}
After the verification of our computational approach based on analytical
solution we can apply our algorithms to evaluate correlation functions for
different porous media images, including real XCT and SEM images. A summary
which contains information about type of the images, dimensions and resolution
can be found in \cref{tab:samples}. XCT images of sandstones are provided by
Digital Rocks Portal\cite{DigitalRocks}. Correlation functions of XCT images
can be seen on \cref{fig:real-xct}.

\begin{table*}[!pt]
  \centering
  \begin{ruledtabular}
    \begin{tabular}{|c|c|c|c|}
      Sample name & Image type & Dimensions (pixels) & Image resolution ($\mu m$) \\
      \hline
      Castlegate sandstone & XCT & $1000 \times 1000 \times 1000$ & 2.25 \\
      Bentheimer sandstone & XCT & $1000 \times 1000 \times 1000$ & 2.25 \\
      Kirby sandstone      & XCT & $1000 \times 1000 \times 1000$ & 2.25 \\
      Sandstone 1 & SEM &  $1280 \times 869$ & 0.10 \\
      Sandstone 2 & SEM &  $1280 \times 869$ & 0.05 \\
      Carbonate 1 & SEM &  $1024 \times 691$ & 0.06
    \end{tabular}
  \end{ruledtabular}
  \caption{Summary of samples used for calculation of correlation functions.}
  \label{tab:samples}
\end{table*}

\begin{figure*}[pt]
  \centering
  \subfigure[Castlegate sandstone]{
    \includegraphics[width=0.3\linewidth]{samples/CastleGate_2d25um_binary.png}
    \label{fig:castlegate}}
  \hfill
  \subfigure[Bentheimer sandstone]{
    \includegraphics[width=0.3\linewidth]{samples/Bentheimer_2d25um_binary.png}
    \label{fig:bentheimer}}
  \hfill
  \subfigure[Kirby sandstone]{
    \includegraphics[width=0.3\linewidth]{samples/Kirby_2d25um_binary.png}
    \label{fig:kirby}}
  \vskip\baselineskip
  \includegraphics[width=0.3\linewidth]{samples/s2-xct.png}
  \includegraphics[width=0.3\linewidth]{samples/c2-xct.png}
  \includegraphics[width=0.3\linewidth]{samples/l2-xct.png}
  \vskip\baselineskip
  \includegraphics[width=0.3\linewidth]{samples/surf2-xct.png}
  \includegraphics[width=0.3\linewidth]{samples/surfvoid-xct.png}
  \caption[]{Visualization of XCT images and plots of correlation functions for
    these images.}
  \label{fig:real-xct}
\end{figure*}
